---
title: "Sci-Fi and Techno Orientalism"
description: |
  Welcome to the website. I hope you enjoy it!
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(plotly)
moviedata <- read_csv(file = "IMDB Movies.csv")
movieplot <- read_csv("wiki_movie_plots_deduped.csv")
JPNgdpdata <- read_csv("export.csv")
CHNgdpdata <- read_csv("exportCHN.csv")
SGPgdpdata <- read_csv("exportSGP.csv")
```

# Science Fiction and Techno Orientalism
### Model
##### The first plot shows the number of science fiction movies each year. Filmmakers' interest in science fiction increased in the 1980s and 1990s.

```{r num_releases}
moviedata %>% 
  select(title, year, genre, country) %>% 
  filter(country == "USA") %>% 
  filter(str_detect(genre, "Sci-Fi")) %>% 
  arrange(year) %>% 
  drop_na(year) %>% 
  mutate(year = as.character(year)) %>% 
  group_by(year) %>% 
  mutate(num_scifi = n()) %>% 
  select(year, num_scifi) %>%
  distinct() %>% 
  ggplot(mapping = aes(x = year,
                       y = num_scifi))+
  geom_col()+
  theme_minimal()+
  scale_x_discrete(breaks = c(1920, 1930, 1940, 1950, 1960, 1970, 1980, 1990, 2000, 2010, 2020))+
  labs(title = "Number of Science Fiction Movies Released in America per Year",
       subtitle = "Interest in science fiction spikes during the 80s and 90s.",
       x = "Year",
       y = "Number of Movies",
       caption = "Source: IMDB")
```

##### The next 3 graphs show GDP of Japan, China, and Singapore, which are countries that often serve as backdrops in science fiction movies. Films such as *Blade Runner* and *Big Hero 6* both model their setting after Japanese cities, and many films use these backdrops to communicate bleak, apocalyptic futures. 

```{r JPNGDP}
JPNgdpdata %>% 
  mutate(`GDP Per Capita` = `GDP Per Capita` / 1000) %>% 
  ggplot(mapping = aes(x = label,
                       y = `GDP Per Capita`))+
  geom_line()+
  scale_x_continuous(breaks = c(1960, 1970, 1980, 1990, 2000, 2010, 2020))+
  labs(title = "Japan's GDP Per Capita (USD)",
       subtitle = "",
       x = "Year",
       y = "GDP Per Capita In Thousands",
       caption = "Source: The World Bank")+
  theme_minimal()
```

```{r CHNGDP}
CHNgdpdata%>% 
  mutate(`GDP Per Capita` = `GDP Per Capita` / 1000) %>% 
  ggplot(mapping = aes(x = label,
                       y = `GDP Per Capita`))+
  geom_line()+
  scale_x_continuous(breaks = c(1960, 1970, 1980, 1990, 2000, 2010, 2020))+
  labs(title = "China's GDP Per Capita (USD)",
       subtitle = "",
       x = "Year",
       y = "GDP Per Capita In Thousands",
       caption = "Source: The World Bank")+
  theme_minimal()
```

```{r SGPGDP}
SGPgdpdata %>% 
  mutate(`GDP Per Capita` = `GDP Per Capita` / 1000) %>% 
  ggplot(mapping = aes(x = label,
                       y = `GDP Per Capita`))+
  geom_line()+
  scale_x_continuous(breaks = c(1960, 1970, 1980, 1990, 2000, 2010, 2020))+
  labs(title = "Singapore's GDP Per Capita (USD)",
       subtitle = "",
       x = "Year",
       y = "GDP Per Capita In Thousands",
       caption = "Source: The World Bank")+
  theme_minimal()
```

#### Some events to note are Japan's economic rise in the 1980's and 1990's, Singapore's growth in the 1990s, and China's growth in the late 2000s. The following graph shows the number of user ratings for each movie, and gives the title, release year, and plot summary. 

```{r num_ratingsdata}
moviedata2 <- moviedata %>% 
  mutate(Title = title)
keywordplot <- merge(moviedata2, movieplot, by = "Title")

``
```


```{r num_ratings}
keywordplotly <- keywordplot %>% 
  select(title, year, genre, country, votes, description) %>% 
  filter(country == "USA") %>% 
  filter(str_detect(genre, "Sci-Fi")) %>% 
  arrange(year) %>% 
  drop_na(year) %>% 
  drop_na(votes) %>% 
  ggplot(mapping = aes(x = year,
                       y = votes,
                       text = paste("Title:", title, "\n", "Plot:", description, "\n", "Year Released:", year)))+
  geom_point()+
  theme_minimal()+
  labs(title = "Number of User Ratings",
       subtitle = "User interest in science fiction increases after the 1980s.",
       x = "Year",
       y = "Number of User Ratings",
       caption = "Source: IMDB")
ggplotly(keywordplotly, tooltip = "text")
```



